\speculake: Hiding Malware in Speculative Execution

### 2018-12-14 paper/architecture.tex
figures and paper pass

We observe that Intel CPUs consider three types of x86\_64 indirect branches:
\texttt{retq}, \texttt{callq *\%rax}, and \texttt{jmpq *\%rax}\footnote{other
general purpose registers besides \texttt{\%rax} can be used as well}. We
created a simple trigger program that performs a series of indirect branches
using \texttt{jmpq *\%rax} instructions.
%, as we found that 28 jumps was the
%minimum needed to reliably train the indirect branch predictor. 
Between each
jump, we incremented \texttt{\%rax} accordingly to continue on to the next jump.
After these jumps, we load a function pointer into \texttt{\%rax} and do a
final indirect branch using \texttt{callq *\%rax}. In our trigger, we perform
these jumps repeatedly in a loop.

@@

We also tested whether instruction complexity or data dependencies impact the
number of instructions that can be completed. We find that data dependencies and
instruction complexity both have an impact on the number of instructions that
can be executed. Instruction complexity is determined by the number of $\mu$~ops
that the instruction uses, which appears to be what is tracked in the ROB. For
instance, on our Skylake architecture, the 64-bit \texttt{idiv} instruction
takes 57~$\mu$~ops, and we can execute up to 3 of them in the speculative world.
Meanwhile, we can execute up to 18 32-bit \texttt{idiv} instructions, which each
take 10~$\mu$~ops~\cite{intel-instruction-tables}. This suggest we can execute
on the order of 175~$\mu$~ops before the speculative world expires.

>>>>

We observe that Intel CPUs consider three types of x86\_64 indirect branches:
\texttt{retq}, \texttt{callq~*\%rax}, and \texttt{jmpq~*\%rax}\footnote{other
general purpose registers besides \texttt{\%rax} can be used as well}. We
created a simple trigger program that performs a series of indirect branches
using \texttt{jmpq~*\%rax} instructions.
%, as we found that 28 jumps was the
%minimum needed to reliably train the indirect branch predictor. 
Between each
jump, we incremented \texttt{\%rax} accordingly to continue on to the next jump.
After these jumps, we load a function pointer into \texttt{\%rax} and do a
final indirect branch using \texttt{callq~*\%rax}. In our trigger, we perform
these jumps repeatedly in a loop.

@@

We also tested whether instruction complexity or data dependencies impact the
number of instructions that can be completed. We find that data dependencies and
instruction complexity both have an impact on the number of instructions that
can be executed. Instruction complexity is determined by the number of $\mu$-ops
that the instruction uses, which appears to be what is tracked in the ROB. For
instance, on our Skylake architecture, the 64-bit \texttt{idiv} instruction
takes 57~$\mu$-ops, and we can execute up to 3 of them in the speculative world.
Meanwhile, we can execute up to 18 32-bit \texttt{idiv} instructions, which each
take 10~$\mu$-ops~\cite{intel-instruction-tables}. This suggest we can execute
on the order of 175~$\mu$-ops before the speculative world expires.

### 2018-12-14 paper/figures.tex
figures and paper pass

\newcommand{\FigHighLevel}{
\begin{figure}[ht]
    \centering
    % \includegraphics[clip, trim=6cm 13.5cm 3.8cm 5cm, width=0.9\linewidth]{figures/exspectre-high-level.pdf}
    \includegraphics[width=0.9\linewidth]{figures/exspectre-high-level-new.pdf}
    \includegraphics[width=0.4\textwidth]{figures/ExSpectre_CR_key.png}
    \caption{\textbf{\speculake}\,---\,%
    Both the trigger and payload binaries exhibit the same initial series of
    indirect jumps (Step 1). The trigger program solely executes these
    jumps to (mis)train the branch predictor. In the Payload program
    \texttt{fn\_ptr} has been set to point to the \texttt{cache\_timing}
    function and flushed from cache. Thus the branch predictor
    mis-predicts the jump to \texttt{cache\_timing} and instead jumps to
    \texttt{target\_fn} (Step 2) as trained by the trigger program (green line). 
    \texttt{target\_fn} then executes speculatively (Step 3), until
    \texttt{fn\_ptr} is loaded from memory and the processor redirects
    computation to the \texttt{cache\_timing} function (Step 4),
    which measures which value was speculatively loaded into cache.}
    \label{fig:high-level}

@@

\newcommand{\FigNestedSpec}{
\begin{figure}[t]
    \centering
    % \includegraphics[clip, trim=6cm 13.5cm 3.8cm 5cm, width=0.9\linewidth]{figures/exspectre-high-level.pdf}
    \includegraphics[width=0.95\linewidth]{figures/ExSpectre_CR_Nested.pdf}
    \caption{\textbf{Nested Speculation}\,---\,%
    Using nested speculation for obfuscated key derivation. The payload uses 
    a sequence of indirect jumps controlled by the trigger to incrementally 
    construct a key exclusively in the speculative environment. Without the 
    trigger an analyst will need to evaluate every ordering of \textbf{all} indirect 
    jumps to reconstruct the key. While the \textit{decryption gadget} may be trivial 
    for an analyst to find, this allows for an encrypted blob in the payload 
    to remain inaccessible in the absence of the trigger. }
    \label{fig:nested-spec}

@@

\newcommand{\FigSpectreOne}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/spectre_1_training.png}
    \caption{\textbf{Speculative buffer overflow warm-up}\,---\,%
    The direct branch predictor must
    be trained to expect that a branch will go a specific way before speculative
    buffer overflows can be used. We varied the number of times a branch was trained
    to be taken and observed the fraction of times we achieved a speculative buffer overflow
    execution immediately after (measured by observing if a speculatively-loaded value was present
    in cache avgeraged over 20,000 trials). We find that a branch must be trained in a
    direction hundreds of times before it can start to be used in a speculative buffer overflow.}
    \label{fig:spectre-one}
\end{figure}
}

@@

\newcommand{\FigSpecMeasureNP}{
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/Speculative_measurements_no-parity.png}
    \caption{\textbf{Speculative limits}\,---\,% To find the number of
    We placed a memory read after an
        increasing number of (speculatively executed) instructions and measured the
        fraction of times the
        loaded value was subsequently in cache. This tells us the upper bound of
        instructions we can reliably execute speculatively. We identify two
        limitations on the speculative lifetime:
        cache miss latency resolving the speculative branch, and the
        CPU's reorder buffer~(ROB) size. We observe that different instructions have
        varying speculative limits: for example, a 32-bit \texttt{idiv} can
        complete only 18 instructions, as each instruction inserts 10-$\mu$-ops
        into the ROB, while cheaper instructions that use fewer $\mu$-ops can execute
        more instructions.}

@@

\newcommand{\FigSpecMeasureParity}{
\begin{figure}[b]
     \centering
        \includegraphics[width=1.05\linewidth]{figures/Speculative_measurements_parity.png}
        \caption{\textbf{Hyperthreading}\,---\,% The trigger program influences
        the payload program via the indirect branch predictor when running on
        the same logical CPU core. Hyperthreads also share an indirect branch
        predictor despite running on different logical cores. We measured the
        impact of same logical core (warm colors) vs parity hyperthreads (cool
        colors, denoted by (P)) on the size of the speculative execution window.
        As hyperthreads run concurrently, they do not need to wait for an OS
        context switch between processes, but the two processes directly contend
        for ROB entries. As a result, we find that hyperthreads generally have a
        smaller speculative execution window.}
    \label{fig:spec-capacity-parity}
\end{figure}
}

@@

\newcommand{\FigCacheMiss}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/cache_miss_dist}
    \caption{\textbf{Cache latency}\,---\,%
        Cumulative distribution function of the cache hit and miss latency
        for an Intel Xeon-1270 and AMD Epyc 7251. If a cache miss is used
        to force CPU speculation, the CPU must wait at least 300-800 cycles
        before the speculated branch can be resolved. However, we find the CPU
        can execute far fewer instructions speculatively, suggesting another
        limit is at play.}
    \label{fig:cache-miss}
\end{figure}
}

\newcommand{\FigGeneralModel}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.4\textwidth]{figures/general_model.pdf}
        \caption{\textbf{ExSpectre model}\,---\,%
        General model of speculative computation within the payload 
        process when triggered. The \textit{Speculative Gadget} has read-only
        access to all memory within the process, but can return updates/results via a
        cache side channel (via access to the \texttt{probe\_array}).
        The process can subsequently make
        \textit{Resultant Computations} based on the value returned from
        the cache side channel to update the state of the \textit{Real World} process.}
    \label{fig:general_model}
\end{figure}
}

@@

\newcommand{\FigSpasmModel}{
\begin{figure}[b]
    \centering
        \includegraphics[width=0.46\textwidth]{figures/spasm_model.pdf}
        \caption{\textbf{SPASM model}\,---\,%
        Our SPASM emulator speculatively decrypts instructions, and emulates
        them in the real world. The \textit{Speculative Computation} decrypts
        the encrypted SPASM binary, returning the result through the side channel
        to allow the \textit{Resultant Computation} to update the emulated state
        (or make system calls) on behalf of the speculative world.}
    \label{fig:spasm_model}
\end{figure}
}

@@

\newcommand{\processorTable}{
\begin{table}
    \centering
    % \resizebox{\linewidth}{!}{\begin{tabularx}{\linewidth}{X X X| Y Y Y}
    \begin{tabularx}{\linewidth}{X b b| Y Y Y}
        \toprule
        \ \newline
        Processor &
        %Year\newline
        \ \newline
        Released &
        Micro- %\newline
        arch. & Nested\newline 
        Spec. &
        Indirect jumps & $\mu$~ops\newline
        (nop)\\
        \hline
        Intel Xeon CPU E3-1276 v3 & 2014 & Haswell &            & 26 & 178\\
        Intel Core i5-7200U       & 2016 & Skylake & \checkmark & 26 & 220\\
        Intel Xeon CPU E3-1270 v6 & 2017 & Skylake & \checkmark & 28 & 220\\
        AMD EPYC 7251             & 2017 & Ryzen   &            & 4  & 178\\
        \toprule
    \end{tabularx}%}
    \caption{\textbf{Processor features}--- We analyzed the capability of
    \speculake on three Intel processors and one AMD. Both Skylake processors
    were capable of nested speculation (Section~\ref{sssec:nested-spec}).
    Indirect jumps is the number of common training indirect jumps needed
    in the trigger program to reliably ($ > 95\%$ of the time) coerce the
    payload program to follow the pattern and jump to the speculative entry
    point specified in the trigger program. $\mu$~ops is the upper bound
    of $\mu$~ops that can be performed speculatively.}

>>>>

\newcommand{\FigHighLevel}{
\begin{figure}[ht]
    \centering
    % \includegraphics[clip, trim=6cm 13.5cm 3.8cm 5cm, width=0.9\linewidth]{figures/exspectre-high-level.pdf}
    \includegraphics[width=0.9\linewidth]{figures/exspectre-high-level-new.pdf}
    \includegraphics[width=0.4\textwidth]{figures/ExSpectre_CR_key.png}
    \caption{\textbf{\speculake}\,---\,%
    Both the trigger and payload binaries perform the same initial series of
    indirect jumps (Step 1), with the goal of having the trigger program
        (mis)train the branch predictor. In the payload program,
    \texttt{fn\_ptr} has been set to point to the \texttt{cache\_timing}
    function but is flushed from cache. Following the pattern in the trigger 
    program, the branch predictor mis-predicts the jump (Step 2) and instead
        speculatively jumps to \texttt{target\_fn} (red line). \texttt{target\_fn}
        briefly executes speculatively (Step 3), until the \texttt{fn\_ptr} is resolved
        and the process redirects computation to the (correct) \texttt{cache\_timing} function
        (Step 4). This function then measures information computed in the speculative
        \texttt{target\_fn} by measuring a covert cache side channel.}
    \label{fig:high-level}

@@

\newcommand{\FigNestedSpec}{
\begin{figure}[t]
    \centering
    % \includegraphics[clip, trim=6cm 13.5cm 3.8cm 5cm, width=0.9\linewidth]{figures/exspectre-high-level.pdf}
    \includegraphics[width=0.95\linewidth]{figures/ExSpectre_CR_Nested.pdf}
    \caption{\textbf{Nested Speculation}\,---\,%
    Some CPUs support nested speculation, allowing the branch predictor to speculate
        a branch while already executing speculatively. We use this to obfuscate \textbf{key
        derivation}. The trigger program executes a sequence of indirect jumps, which
        the payload program will follow speculatively. Each jump target in the
        payload program will add a small number of bits to a speculatively-computed
        key. Without knowing the exact pattern of jump targets (specified only in the
        trigger program), the analyst will be unable to determine the key when a sufficient
        speculative depth/number of targets is used. In our implementation, we used a
        speculative depth of 16 with $2^8$ targets to derive a 128-bit key. While the \textit{decryption gadget} may
        be easy for an analyst to find, without the key, the encrypted data remains
        inaccesible.}
    \label{fig:nested-spec}

@@

\newcommand{\FigSpectreOne}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/spectre_1_training.png}
    \caption{\textbf{Speculative buffer overflow warm-up}\,---\,%
    The direct branch predictor must
    be trained to expect that a branch will go a specific way before speculative
    buffer overflows can be used. We varied the number of times a branch was trained
    to be taken and observed the fraction of times we achieved a speculative buffer overflow
    execution immediately after (measured by observing if a speculatively-loaded value was present
    in cache avgeraged over 20,000 trials). We find that a branch must be trained in a
    direction hundreds of times before it can be reliably used in a speculative buffer overflow.}
    \label{fig:spectre-one}
\end{figure}
}

@@

\newcommand{\FigSpecMeasureNP}{
\begin{figure*}[t]
    \centering
    \includegraphics[width=0.9\textwidth]{figures/Speculative_measurements_no-parity.png}
    \caption{\textbf{Speculative limits}\,---\,% To find the number of
    We placed a memory read after an
        increasing number of (speculatively executed) instructions and measured the
        fraction of times the
        loaded value was subsequently in cache. This tells us the upper bound of
        instructions we can reliably execute speculatively. We identify two
        limitations on the speculative lifetime:
        cache miss latency resolving the speculative branch, and the
        CPU's reorder buffer~(ROB) size. We observe that different instructions have
        varying speculative limits: for example, a 32-bit \texttt{idiv} can
        complete only 18 instructions, as each instruction inserts 10 $\mu$-ops
        into the ROB, while cheaper instructions that use fewer $\mu$-ops can execute
        more instructions.}

@@

\newcommand{\FigSpecMeasureParity}{
\begin{figure}[b]
     \centering
        \includegraphics[width=1.05\linewidth]{figures/Speculative_measurements_parity.png}
        \caption{\textbf{Hyperthreading}\,---\,% The trigger program influences
        We measured the impact hyperthreading has on speculative execution.
        Trigger and payload programs running on the same logical core require
        a context switch to alternate processes, but allows each to have full
        utilization of the ROB and execution units when they run.
        Running the programs on parity hyperthreads (denoted by (P))
        allows them to run simultaneously without context switching,
        but we observe this configuration effectively halves the amount that
        each program can speculatively execute, suggesting that hyperthreads share
        parts of the ROB or execution units.}
    \label{fig:spec-capacity-parity}
\end{figure}
}

@@

\newcommand{\FigCacheMiss}{
\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/cache_miss_dist}
    \caption{\textbf{Cache latency}\,---\,%
        Cumulative distribution function of the cache hit and miss latency
        for an Intel Xeon-1270 and AMD Epyc 7251. If a cache miss is used
        to force CPU speculation, the CPU must wait at least 300-800 cycles
        before the speculated branch can be resolved. However, we find the CPU
        is occasionally limited to far fewer instructions speculatively, suggesting another
        limit is at play.}
    \label{fig:cache-miss}
\end{figure}
}

\newcommand{\FigGeneralModel}{
\begin{figure}[t]
    \centering
        \includegraphics[width=0.4\textwidth]{figures/general_model.pdf}
        \caption{\textbf{ExSpectre model}\,---\,%
        General model of speculative computation within the payload 
        process when triggered. The \textit{Speculative Gadget} has read-only
        access to all memory within the process, but can only return updates/results via a
        cache side channel (by accessing the \texttt{probe\_array}).
        The process can subsequently
        \textit{Reload} from the cache side channel to learn the speculatively-computed result,
        and update the state of the \textit{Real World} process.}
    \label{fig:general_model}
\end{figure}
}

@@

\newcommand{\FigSpasmModel}{
\begin{figure}[b]
    \centering
        \includegraphics[width=0.46\textwidth]{figures/spasm_model.pdf}
        \caption{\textbf{SPASM model}\,---\,%
        Our SPASM emulator speculatively decrypts instructions, and emulates
        them in the real world. The \textit{Speculative Computation} decrypts
        the encrypted SPASM binary using AES, returning the result through the side channel
        to allow the \textit{Real World} to update the emulated state
        and make system calls on behalf of the speculative world.}
    \label{fig:spasm_model}
\end{figure}
}

@@

\newcommand{\processorTable}{
\begin{table}
    \centering
    % \resizebox{\linewidth}{!}{\begin{tabularx}{\linewidth}{X X X| Y Y Y}
    \begin{tabularx}{\linewidth}{X b b| Y Y Y}
        \toprule
        \ \newline
        Processor &
        %Year\newline
        \ \newline
        Released &
        Micro- %\newline
        arch. & Nested\newline 
        Spec. &
        Indirect jumps & $\mu$-ops\newline
        (nop)\\
        \hline
        Intel Xeon CPU E3-1276 v3 & 2014 & Haswell &            & 26 & 178\\
        Intel Core i5-7200U       & 2016 & Skylake & \checkmark & 26 & 220\\
        Intel Xeon CPU E3-1270 v6 & 2017 & Skylake & \checkmark & 28 & 220\\
        AMD EPYC 7251             & 2017 & Ryzen   &            & 4  & 178\\
        \toprule
    \end{tabularx}%}
    \caption{\textbf{Processor features}--- We analyzed the capability of
    \speculake on three Intel processors and one AMD. Both Skylake processors
    were capable of nested speculation (Section~\ref{sssec:nested-spec}).
    Indirect jumps is the number of common training indirect jumps needed
    in the trigger program to reliably ($ > 95\%$ of the time) coerce the
    payload program to follow the pattern and jump to the speculative entry
    point specified in the trigger program. $\mu$-ops is the upper bound
    of $\mu$-ops that can be performed speculatively.}

### 2018-12-14 paper/implementation.tex
figures and paper pass

\subsection{AES Decryption}
\label{subsec:impl-aes}
The speculative world is able to take advantage of the AES-NI instructions to
decrypt messages. However, the speculative upper-limit of about 175 $\mu$~ops is
not enough to allow us to compute the key expansion, even using the
\texttt{aeskeygenassist} instructions. To avoid this, we can either preload the
expanded key schedule into the program (instead of the key), or use a cheaper
(non-standard) key expansion algorithm. For the former, we note that an analyst
could observe the structure of a normal key schedule, but we can avoid this by
simply selecting 11 random round keys. We note that this should not weaken the
security of AES, as we can ensure the round keys are not linearly related.

@@

% TODO: this could move elsewhere?
We demonstrate the speed that information can be decrypted via the speculative
world, and we vary the channel width of the side channel from 1 to 12 bits to
measure its performance. At low channel width, reading from the cache side
channel requires timing reads from only 2 locations, while at 12-bits, the side
channel requires reading $2^{12}$ locations. On the other hand, there is a fixed
overhead per speculative iteration that favors increased channel width to
maximize bandwidth. As shown in Figure~\ref{fig:spec_bandwidth}, 8 bits is the
optimal side channel width, allowing us to decrypt over 5,000 bits per second
(625 Bytes/sec). We note an improvement over this rate by loading multiple
values into the probe array during speculation. Instead of a single
probe array of 1024 entries communicating 10-bits, we can split the array into
four sections of 256 entries each, and signal four times (one per section) during
speculation. This provides a 32-bit channel overall, while only having to probe
1024 entries. This method is limited by the limited $\mu$~operation budget,
however, our implementation using these parameters (four sections of 256
entries) is able to decrypt over 11~Kbps (1,425 Bytes/sec).

@@

We used 6 bits in the construction of this instruction set as our goal is to
limit the length of each opcode as much as possible. Note that this is different
from the goal in maximizing bandwidth, as our goal now is to maximize
instruction throughput. Given our short instructions, loading values into
registers requires shifting in 4-bits at a time. SPASM has two registers that
act as a pointer and working register, that can be used to perform jumps,
arbitrary memory reads and writes, and basic arithmetic. We also have a
\texttt{syscall} instruction that makes a real system call to the underlying
operating system with parameters loaded from the SPASM state, allowing us to
interact with the real world. Details of the SPASM instruction set can be found
in Appendix~\ref{appendix:spasm}.

@@

We discovered a candidate that corresponds to code in OpenSSL's
\texttt{nistp256.c} that contained 31 indirect jumps repeated 254 times each
handshake. This code is used during the TLS key exchange as the server computes
the ECDHE shared secret. We made a list of 31 source-destination address pairs
for these indirect jumps, and constructed a \texttt{jump}/\texttt{ret} chain to
mimic the same jump pattern in our payload program. Our payload program mimics
the first 30 indirect jump source/destination pairs, with a final jump going to
a cache timing function in our payload program. However, due to the prior
pattern, this last jump is frequently mis-speculated (about 3.5\% of the time),
and instead goes to the destination corresponding to the 31st jump in OpenSSL,
which serves as our speculative entry point.

>>>>

\subsection{AES Decryption}
\label{subsec:impl-aes}
The speculative world is able to take advantage of the AES-NI instructions to
decrypt messages. However, the speculative upper-limit of about 175 $\mu$-ops is
not enough to allow us to compute the key expansion, even using the
\texttt{aeskeygenassist} instructions. To avoid this, we can either preload the
expanded key schedule into the program (instead of the key), or use a cheaper
(non-standard) key expansion algorithm. For the former, we note that an analyst
could observe the structure of a normal key schedule, but we can avoid this by
simply selecting 11 random round keys. We note that this should not weaken the
security of AES, as we can ensure the round keys are not linearly related.

@@

% TODO: this could move elsewhere?
We demonstrate the speed that information can be decrypted via the speculative
world, and we vary the channel width of the side channel from 1 to 12 bits to
measure its performance. At low channel width, reading from the cache side
channel requires timing reads from only 2 locations, while at 12-bits, the side
channel requires reading $2^{12}$ locations. On the other hand, there is a fixed
overhead per speculative iteration that favors increased channel width to
maximize bandwidth. As shown in Figure~\ref{fig:spec_bandwidth}, 8 bits is the
optimal side channel width, allowing us to decrypt over 5,000 bits per second
(625 Bytes/sec). We note an improvement over this rate by loading multiple
values into the probe array during speculation. Instead of a single
probe array of 1024 entries communicating 10-bits, we can split the array into
four sections of 256 entries each, and signal four times (one per section) during
speculation. This provides a 32-bit channel overall, while still only having to probe
1024 entries. This method is capped by the limited $\mu$-operation budget,
however our implementation using these parameters (four sections of 256
entries) is able to decrypt over 11~Kbps (1,425 Bytes/sec).

@@

We used 6 bits in the construction of this instruction set as our goal is to
limit the length of each opcode as much as possible. Note that this is different
from the goal in maximizing bandwidth, as our goal now is to maximize
instruction throughput. Given our short instructions, loading values into
registers requires shifting in 4-bits at a time. SPASM has two registers that
act as a pointer and working register, that can be used to perform jumps,
arbitrary memory reads and writes, and basic arithmetic. We also have a
\texttt{syscall} instruction that makes a real system call to the underlying
operating system with parameters loaded from the SPASM state, allowing us to
interact with the real world. 
%Details of the SPASM instruction set can be found
%in Appendix~\ref{appendix:spasm}.

@@

We discovered a candidate that corresponds to code in OpenSSL's
\texttt{nistp256.c} that contained 31 indirect jumps repeated 254 times each
handshake. This code is used during the TLS key exchange as the server computes
the ECDHE shared secret. We made a list of 31 source-destination address pairs
for these indirect jumps, and constructed a \texttt{jump}/\texttt{ret} chain to
mimic the same jump pattern in our payload program. Our payload program mimics
the first 30 indirect jump source/destination pairs, with a final jump going to
a cache timing function in our payload program. However, due to the prior
pattern, this last jump is frequently mis-speculated (about 3.5\% of the time),
and instead goes to the destination corresponding to the 31\textsuperscript{st} jump in OpenSSL,
which serves as our speculative entry point.
